Report

### 2021-01-20 report.Rmd
Add eveness to the analysis

```{r, cache = FALSE}
loadd(log_bm_net_group_f3y, model_log_bm_f3y,
  summary_log_bm_f3y, vif_log_bm_f3y)
#loadd(bm_net_group_median, bm_vs_net_trends)
loadd(bm_net_group_f3y)
loadd(bm_net_group_f3y)
loadd(rich_vs_net_trends)

#compute_my_lm_vs_net_model(
      #.df = filter(my_bm_net_group, !is.na(protocol_type)),
      #var_to_group = "variable"
#)
```

#### All protocol

```{r, eval = TRUE}
#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
#loadd(model_log_bm_f3y_table_medium)
#model_log_bm_f3y_table_medium[["reg_table"]] %>% 
  #filter(y %in% get_com_str_var(all = FALSE)) %>%
  #kable(.,
    #booktabs = TRUE, 
    #caption = 
      #paste0(
      #"Regression table for the model: dN =",
      #"dB + B + dB*B + Inc*B + dB*Inc*B."
    #)) %>% 
  #kable_styling(latex_options =c("scale_down", "stripped")) %>%
  #collapse_rows(columns = 1, valign = "top")
```

```{r}
#model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  #filter(variable %in% get_com_str_var(all = FALSE)) %>%
  #kable(., booktabs = TRUE,
    #caption = 
      #paste0(
      #"ANOVA table for the model: dN =",
      #"dB + B + dB*B + Inc*B + dB*Inc*B."
    #)
  #) %>%
  #kable_styling(latex_options =c("scale_down", "stripped")) %>%
  #collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
loadd(predict_plot)
pred_plot_signif_com <- predict_plot %>%
  filter(
    y %in% c(get_com_str_var(), "ct_ff", "log_rich_std"),
    x == "log_bm_std"
  )
legend_signif <- get_legend(
  pred_plot_signif_com$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_signif_com$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_signif_com$pred_plot,
  labels = pred_plot_signif_com$y, nrow = 1
)
pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_rich <- predict_plot %>%
  filter( y %in% c(get_com_str_var(), "ct_ff"), x == "log_rich_std") %>%
  filter(!y %in% "rich_std")
legend_signif <- get_legend(
  pred_plot_rich$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_rich$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_rich$pred_plot,
  labels = pred_plot_rich$y
)
pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

>>>>

@@

```{r}
loadd(predict_plot)
pred_plot_signif_com <- predict_plot %>%
  filter(
    y %in% c(get_com_str_var(), "log_rich_std"),
    x == "log_bm_std"
  )
legend_signif <- get_legend(
  pred_plot_signif_com$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_signif_com$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_signif_com$pred_plot,
  labels = pred_plot_signif_com$y, nrow = 1
)
pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_rich <- predict_plot %>%
  filter( y %in% c(get_com_str_var(), "bm_std", "log_bm_std"), x == "log_rich_std") %>%
  filter(!y %in% "rich_std")
legend_signif <- get_legend(
  pred_plot_rich$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_rich$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_rich$pred_plot,
  labels = pred_plot_rich$y
)
pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```
